NumPy---Array Programming in Python

### 2020-01-26 body.tex
Add ecosystem figure

The scientific Python ecosystem \fixme{(Fig.)} is composed of many different libraries.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
Matplotlib generates publication-ready figures and visualizations.
Employing these array-aware libraries are widely used
technique-specific libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11}
and several domain-specific
libraries \cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}.
This has made the scientific Python ecosystem popular for scientific
research.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.48\textwidth]{static/ecosystem}
  \caption{\textbf{Scientific Python Ecosystem.}
   }
  \label{fig:ecosystem}
\end{figure}

The scientific Python ecosystem (Fig.~\ref{fig:ecosystem}) is composed of many different libraries.
SciPy provides fundamental algorithms for scientific computing on arrays
including many mathematical, scientific, and engineering routines.
SciPy and NumPy are closely related and were developed together often
by the same people.
Matplotlib generates publication-ready figures and visualizations.
Employing these array-aware libraries are widely used
technique-specific libraries\cite{pedregosa2011scikit,vanderwalt2014scikit,SciPyProceedings_11}
and several domain-specific projects and
libraries \cite{astropy:2013,astropy:2018,cock2009biopython,millman2007analysis,2018EGUGA..2012146H}.
This has made the scientific Python ecosystem popular for scientific
research.
